Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-15 paper.qmd
Changed axis text sizes

axis_scale <- 2 * limits/3
axis_pos <- -0.5 * limits

@@

scurve_proj1_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696") + 
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50")

@@

axis_scale <- 2 * limits/3
axis_pos <- -0.5 * limits

@@

scurve_proj2_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696") + 
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50")

@@

```{r}
#| label: s-curve-true-model-proj3

@@

axis_scale <- 2 * limits/3
axis_pos <- -0.5 * limits

@@

@@

scurve_proj1_true_model + scurve_proj2_true_model + 
  scurve_proj3_true_model + plot_layout(ncol = 3)
```

>>>>

axis_scale <- 2 * limits/3
axis_pos <- -0.6 * limits

@@

scurve_proj1_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696") + 
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 2.5)

@@

axis_scale <- 2 * limits/3
axis_pos <- -0.4 * limits

@@

scurve_proj2_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696") + 
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 2.5)

@@

```{r}
#| label: s-curve-true-model-proj3
#| eval: false

@@

limits <- 1.5
rng <- range(projected)
projected <- projected/max(abs(rng))
colnames(projected) <- c("P1", "P2")
projected <- data.frame(projected)
obs_labels <- as.character(1:nrow(training_data_scurve))

axis_scale <- 2 * limits/3
axis_pos <- -2/3 * limits

@@

# theta <- seq(0, 2 * pi, length = 50)
# circle <- data.frame(c1 = adj(cos(theta)), c2 = adj(sin(theta)))

@@

scurve_proj1_true_model + scurve_proj2_true_model + 
  plot_layout(ncol = 2)
```
